Examples in R* paper

### 2020-03-16 src/s_examples.Rmd
started discussion

---
title: "Fake data"
output: html_notebook
---

@@

# AR1 examples
```{r}
f_ar1 <- function(rho, sigma, L){
  x <- vector(length = L)
  x[1] <- rnorm(1, 0, sd=sigma)
  for(i in 2:L)
    x[i] = rho * x[i - 1] + rnorm(1, 0, sd=sigma)
  return(x)
}
plot(f_ar1(1.0, 1, 100), type='l')

@@

Test LDA on classifying chains
```{r}
full_data <- f_generate_lower_var_four(1/3, 0.3, 1, 1000) %>% 
  melt() %>% 
  rename(iter=Var1,
         chain=Var2) %>% 
  dplyr::select(-iter)
rand_samples <- sample(1:nrow(full_data), 0.7 * nrow(full_data))
training_data <- full_data[rand_samples, ]
testing_data <- full_data[-rand_samples, ]
require(MASS)
fitter <- lda(formula = chain ~ ., 
         data = training_data, 
         prior = c(1,1,1,1)/4)
plda <- predict(object=fitter, newdata=testing_data)
tibble(predicted=plda$class, actual=testing_data$chain) %>% 
  mutate(correct=if_else(predicted==actual, 1, 0)) %>% 
  summarise(mean(correct))
```

Try Caret
```{r}
library(caret)
library(gbm)
# add in extra column of nonsense values since the 
full_data <- full_data %>% 
  mutate(chain=as.factor(chain)) %>% 
  mutate(ones=rnorm(nrow(full_data)))
training_data <- full_data[rand_samples, ]
testing_data <- full_data[-rand_samples, ]

caretGrid <- expand.grid(interaction.depth=c(3), n.trees = 50,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
gbmFit1 <- train(chain ~ ., data = training_data, 
                 method = "gbm",
                 trControl = trainControl(method = 'none'), 
                    tuneGrid = caretGrid)
# plot(gbmFit1)
plda <- predict(object=gbmFit1, newdata=testing_data)
tibble(predicted=plda, actual=testing_data$chain) %>% 
  mutate(correct=if_else(predicted==actual, 1, 0)) %>% 
  summarise(mean(correct))
varImp(gbmFit1)

# plot predictions as fn of value
testing_data %>% 
  arrange(value) %>% 
  mutate(predictions=predict(object=gbmFit1, .)) %>% 
  ggplot(aes(x=value, y=predictions)) +
  geom_jitter()
```

@@

Trying probabilistic prediction
```{r}
full_data <- f_generate_lower_var_four(1/3, 0.3, 1, 1000) %>% 
  melt() %>% 
  rename(iter=Var1,
         chain=Var2) %>% 
  dplyr::select(-iter)
rand_samples <- sample(1:nrow(full_data), 0.7 * nrow(full_data))
full_data <- full_data %>% 
    mutate(chain=as.factor(chain)) %>% 
    mutate(ones=rnorm(nrow(full_data)))
training_data <- full_data[rand_samples, ]
testing_data <- full_data[-rand_samples, ]

@@

nsim <- 1000
mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
hist(colMeans(mAccuracy)/0.25)

@@

# saveRDS(tibble(unconverged=colMeans(mAccuracy)/0.25,
#        converged=colMeans(mAccuracy1)/0.25),
#        "../output/ar1_two_replicates.rds")
mAR1 <- readRDS("../output/ar1_two_replicates.rds")
g3 <- 
  mAR1 %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series") +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("C.") +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8))

@@

@@

Run model
```{r}
fit_cp <- sampling(
  model_cp, data = eight_schools,
  iter = 2000, chains = 4, seed = 483892929, refresh = 0,
  control = list(adapt_delta = 0.95)
)

@@

## Break each chain into two then make flattened data
## Centered
```{r}
full_data_all <- rstan::extract(fit_cp, permuted=F)
full_data <- array(dim=c(500, 8, 11))
k <- 1
for(i in 1:4){
  first_half <- full_data_all[1:500, i, ]
  second_half <- full_data_all[501:1000, i, ]
  full_data[, k, ] <- first_half
  k <- k + 1
  full_data[, k, ] <- second_half
  k <- k + 1
}

@@

nsim <- 1000
mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
hist(colMeans(mAccuracy)/0.125)
mAccuracy_centered <- mAccuracy
```

```{r}
full_data_all <- rstan::extract(fit_ncp, permuted=F)
nparams <- 19
full_data <- array(dim=c(500, 8, nparams))
k <- 1
for(i in 1:4){
  first_half <- full_data_all[1:500, i, ]
  second_half <- full_data_all[501:1000, i, ]
  full_data[, k, ] <- first_half
  k <- k + 1
  full_data[, k, ] <- second_half
  k <- k + 1
}

@@

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
hist(colMeans(mAccuracy)/0.125)
mAccuracy_noncentered <- mAccuracy
```

```{r}
# saveRDS(tibble(centered=colMeans(mAccuracy_centered)/0.125,
#        non_centered=colMeans(mAccuracy_noncentered)/0.125),
#        "../output/eight_schools_replicates.rds")
tibble(centered=colMeans(mAccuracy_centered)/0.125,
       non_centered=colMeans(mAccuracy_noncentered)/0.125) %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("C.") +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8))
```

@@

nsim <- 1000
mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
hist(colMeans(mAccuracy)/(1/n_distinct(training_data$chain)))
mAccuracy_centered <- mAccuracy

@@

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
hist(colMeans(mAccuracy)/(1/n_distinct(training_data$chain)))
mAccuracy_noncentered <- mAccuracy
```

```{r}
a_df <- tibble(centered=colMeans(mAccuracy_centered)/(1/n_distinct(training_data$chain)),
       non_centered=colMeans(mAccuracy_noncentered)/(1/n_distinct(training_data$chain)))
saveRDS(a_df, "../output/eight_schools_replicates_4.rds")
a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("C.") +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8))
```

Trying original data with index variables
```{r}
full_data <- rstan::extract(fit_cp, permuted=F)
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = 13)
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:11] <- full_data[j, i, ]
    if(j < (nrow(full_data)/2))
      m_flattened[k, 12] <- 0
    else
      m_flattened[k, 12] <- 1
    m_flattened[k, 13] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V13) %>% 
  mutate(chain=as.factor(chain))

nsim <- 1000
mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
hist(colMeans(mAccuracy)/(1/n_distinct(training_data$chain)))
mAccuracy_centered <- mAccuracy

full_data <- rstan::extract(fit_ncp, permuted=F)
k <- 1
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams+2))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    if(j < (nrow(full_data)/2))
      m_flattened[k, (nparams+1)] <- 0
    else
      m_flattened[k, (nparams+1)] <- 1
    m_flattened[k, (nparams+2)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V21) %>% 
  mutate(chain=as.factor(chain))

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
hist(colMeans(mAccuracy)/(1/n_distinct(training_data$chain)))
mAccuracy_noncentered <- mAccuracy
```

```{r}
a_df <- tibble(centered=colMeans(mAccuracy_centered)/(1/n_distinct(training_data$chain)),
       non_centered=colMeans(mAccuracy_noncentered)/(1/n_distinct(training_data$chain)))
saveRDS(a_df, "../output/eight_schools_replicates_4_index.rds")
a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("C.") +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8))
```

Three uncertainty distributions
```{r}
a_df <- readRDS("../output/eight_schools_replicates.rds")
g1 <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  xlim(0.78, 1.6) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("A.") +
  theme(text = element_text(size=14, colour="black"),
        legend.position = "none")
a_df <- readRDS("../output/eight_schools_replicates_4.rds")
g2 <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlim(0.78, 1.6) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("B.") +
  theme(text = element_text(size=14, colour="black"))
a_df <- readRDS("../output/eight_schools_replicates_4_index.rds")
g3 <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("C.") +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8))

@@

# Cauchy example
```{r}
fit_nom <- stan(file = 'cauchy_nom.stan', seed = 7878, refresh = 0)
full_data <- rstan::extract(fit_nom, permuted=F)
nparams <- 52
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams + 1))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    m_flattened[k, (nparams+1)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V53) %>% 
  mutate(chain=as.factor(chain))
n_distinct(m_flattened$chain)

```{r}
fit_alt1 <- stan(file = 'cauchy_alt_1.stan', seed = 7878, refresh = 0)
full_data <- rstan::extract(fit_alt1, permuted=F)
nparams <- dim(full_data)[3]
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams + 1))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    m_flattened[k, (nparams+1)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V153) %>% 
  mutate(chain=as.factor(chain))
n_distinct(m_flattened$chain)

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
hist(colMeans(mAccuracy)/(1/n_distinct(training_data$chain)))
mAccuracy_alt_1 <- mAccuracy
```

```{r}
a_df <- tibble(nominal=colMeans(mAccuracy_nom)/(1/n_distinct(training_data$chain)),
               alt=colMeans(mAccuracy_alt_1)/(1/n_distinct(training_data$chain)))
saveRDS(a_df, "../output/cauchy.rds")
a_df <- readRDS("../output/cauchy.rds")

## More iterations
```{r}
fit_nom <- stan(file = 'cauchy_nom.stan', seed = 7878, refresh = 0, iter = 10000,
                thin = 5)
full_data <- rstan::extract(fit_nom, permuted=F)
nparams <- 52
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams + 1))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    m_flattened[k, (nparams+1)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V53) %>% 
  mutate(chain=as.factor(chain))
n_distinct(m_flattened$chain)

```{r}
fit_alt1 <- stan(file = 'cauchy_alt_1.stan', seed = 7878, refresh = 0, iter = 10000,
                thin = 5)
full_data <- rstan::extract(fit_alt1, permuted=F)
nparams <- dim(full_data)[3]
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams + 1))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    m_flattened[k, (nparams+1)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V153) %>% 
  mutate(chain=as.factor(chain))
n_distinct(m_flattened$chain)

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
hist(colMeans(mAccuracy)/(1/n_distinct(training_data$chain)))
mAccuracy_alt_1 <- mAccuracy
```

```{r}
a_df <- tibble(nominal=colMeans(mAccuracy_nom)/(1/n_distinct(training_data$chain)),
               alt=colMeans(mAccuracy_alt_1)/(1/n_distinct(training_data$chain)))
saveRDS(a_df, "../output/cauchy_more_iter.rds")
a_df <- readRDS("../output/cauchy.rds")

a_df <- readRDS("../output/cauchy_more_iter.rds")

g2 <-
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Parameterisation", labels=c("nominal", "alternative")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black")) +
  ggtitle("B.")
g2

>>>>

---
title: "Examples in R* paper"
author: "Ben Lambert"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_notebook
---

@@

# AR1 example
Functions to generate simulated data
```{r}
f_ar1 <- function(rho, sigma, L){
  x <- vector(length = L)
  x[1] <- rnorm(1, 0, sd=sigma)
  for(i in 2:L)
    x[i] = rho * x[i - 1] + rnorm(1, 0, sd=sigma)
  return(x)
}

@@

Use gbm model in Caret to predict chain identity
```{r}
library(caret)
library(gbm)

# generate data
full_data <- f_generate_lower_var_four(1/3, 0.3, 1, 1000) %>% 
  melt() %>% 
  rename(iter=Var1,
         chain=Var2) %>% 
  dplyr::select(-iter)

# add in extra column of nonsense values since gbm needs 2+ vars
full_data <- full_data %>% 
  mutate(chain=as.factor(chain)) %>% 
  mutate(ones=rnorm(nrow(full_data)))

# create training/testing data
rand_samples <- sample(1:nrow(full_data), 0.7 * nrow(full_data))
training_data <- full_data[rand_samples, ]
testing_data <- full_data[-rand_samples, ]

caretGrid <- expand.grid(interaction.depth=c(3), n.trees = 50,
                   shrinkage=c(0.1),
                   n.minobsinnode=10)
gbmFit1 <- train(chain ~ ., data = training_data, 
                 method = "gbm",
                 trControl = trainControl(method = 'none'), 
                    tuneGrid = caretGrid)
# plot(gbmFit1)
plda <- predict(object=gbmFit1, newdata=testing_data)
tibble(predicted=plda, actual=testing_data$chain) %>% 
  mutate(correct=if_else(predicted==actual, 1, 0)) %>% 
  summarise(mean(correct))

# plot predictions as fn of value
testing_data %>% 
  arrange(value) %>% 
  mutate(predictions=predict(object=gbmFit1, .)) %>% 
  ggplot(aes(x=value, y=predictions)) +
  geom_jitter() +
  coord_flip()
```

@@

Generate R* distribution based on 1000 iterations
```{r}
full_data <- f_generate_lower_var_four(1/3, 0.3, 1, 1000) %>% 
  melt() %>% 
  rename(iter=Var1,
         chain=Var2) %>% 
  dplyr::select(-iter)
rand_samples <- sample(1:nrow(full_data), 0.7 * nrow(full_data))
full_data <- full_data %>% 
    mutate(chain=as.factor(chain)) %>% 
    mutate(ones=rnorm(nrow(full_data)))
training_data <- full_data[rand_samples, ]
testing_data <- full_data[-rand_samples, ]

@@

nsim <- 10
mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}

@@

mAR1 <- tibble(unconverged=colMeans(mAccuracy)/0.25,
               converged=colMeans(mAccuracy1)/0.25)
g3 <- 
  mAR1 %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series") +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("C.") +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8))

@@

# Multivariate normal

Fit model in Stan
```{r}
N <- 250
A <- rWishart(1, 250, diag(N))[,,1]
model <- stan_model("mvt_250.stan")
fit <- sampling(model, data=list(N=N, A=A), iter=200, chains=4)
print(fit)
```

```{r}
full_data <- rstan::extract(fit, permuted=F)
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = 252)
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:251] <- full_data[j, i, ]
    m_flattened[k, 252] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V252) %>% 
  mutate(chain=as.factor(chain))

plda <- predict(object=gbmFit1, newdata=testing_data)
tibble(predicted=plda, actual=testing_data$chain) %>% 
  mutate(correct=if_else(predicted==actual, 1, 0)) %>% 
  summarise(mean(correct))
varImp(gbmFit1)
```

# Cauchy example

Generate R* distribution from nominal Cauchy fit
```{r}
nsim <- 1000
fit_nom <- stan(file = 'cauchy_nom.stan', seed = 7878, refresh = 0)
full_data <- rstan::extract(fit_nom, permuted=F)
nparams <- 52
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams + 1))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    m_flattened[k, (nparams+1)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V53) %>% 
  mutate(chain=as.factor(chain))
n_distinct(m_flattened$chain)

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
mAccuracy_nom <- mAccuracy
```

Generate R* distribution from alternative Cauchy parameterisation
```{r}
fit_alt1 <- stan(file = 'cauchy_alt_1.stan', seed = 7878, refresh = 0)
full_data <- rstan::extract(fit_alt1, permuted=F)
nparams <- dim(full_data)[3]
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams + 1))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    m_flattened[k, (nparams+1)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V153) %>% 
  mutate(chain=as.factor(chain))
n_distinct(m_flattened$chain)

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
mAccuracy_alt_1 <- mAccuracy
```

```{r}
a_df <- tibble(nominal=colMeans(mAccuracy_nom)/(1/n_distinct(training_data$chain)),
               alt=colMeans(mAccuracy_alt_1)/(1/n_distinct(training_data$chain)))

## More iterations
Nominal model with 10000 iterations and thinning by 10
```{r}
fit_nom <- stan(file = 'cauchy_nom.stan', seed = 7878, refresh = 0, iter = 10000,
                thin = 5)
full_data <- rstan::extract(fit_nom, permuted=F)
nparams <- 52
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams + 1))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    m_flattened[k, (nparams+1)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V53) %>% 
  mutate(chain=as.factor(chain))
n_distinct(m_flattened$chain)

Alternative model with 10000 iterations and thinning by 10
```{r}
fit_alt1 <- stan(file = 'cauchy_alt_1.stan', seed = 7878, refresh = 0, iter = 10000,
                thin = 5)
full_data <- rstan::extract(fit_alt1, permuted=F)
nparams <- dim(full_data)[3]
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams + 1))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    m_flattened[k, (nparams+1)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V153) %>% 
  mutate(chain=as.factor(chain))
n_distinct(m_flattened$chain)

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
mAccuracy_alt_1 <- mAccuracy
```

Plot
```{r}
b_df <- tibble(nominal=colMeans(mAccuracy_nom)/(1/n_distinct(training_data$chain)),
               alt=colMeans(mAccuracy_alt_1)/(1/n_distinct(training_data$chain)))

g2 <-
  b_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Parameterisation", labels=c("nominal", "alternative")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black")) +
  ggtitle("B.")
g2

@@

Run models
```{r}
fit_cp <- sampling(
  model_cp, data = eight_schools,
  iter = 2000, chains = 4, seed = 483892929, refresh = 0,
  control = list(adapt_delta = 0.95)
)

@@

## Break each chain into two then make flattened data
Centered
```{r}
full_data_all <- rstan::extract(fit_cp, permuted=F)
full_data <- array(dim=c(500, 8, 11))
k <- 1
for(i in 1:4){
  first_half <- full_data_all[1:500, i, ]
  second_half <- full_data_all[501:1000, i, ]
  full_data[, k, ] <- first_half
  k <- k + 1
  full_data[, k, ] <- second_half
  k <- k + 1
}

@@

nsim <- 1000
mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
mAccuracy_centered <- mAccuracy
```

Noncentered
```{r}
full_data_all <- rstan::extract(fit_ncp, permuted=F)
nparams <- 19
full_data <- array(dim=c(500, 8, nparams))
k <- 1
for(i in 1:4){
  first_half <- full_data_all[1:500, i, ]
  second_half <- full_data_all[501:1000, i, ]
  full_data[, k, ] <- first_half
  k <- k + 1
  full_data[, k, ] <- second_half
  k <- k + 1
}

@@

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
mAccuracy_noncentered <- mAccuracy
```

Store both
```{r}
c_df <- tibble(centered=colMeans(mAccuracy_centered)/0.125,
       non_centered=colMeans(mAccuracy_noncentered)/0.125)
```

@@

nsim <- 1000
mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
mAccuracy_centered <- mAccuracy

@@

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}
mAccuracy_noncentered <- mAccuracy
```

```{r}
d_df <- tibble(centered=colMeans(mAccuracy_centered)/(1/n_distinct(training_data$chain)),
       non_centered=colMeans(mAccuracy_noncentered)/(1/n_distinct(training_data$chain)))
```

Plot two R* distributions
```{r}
g1 <- 
  c_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  xlim(0.78, 1.6) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("A.") +
  theme(text = element_text(size=14, colour="black"),
        legend.position = "none")
g2 <- 
  d_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8) +
  scale_fill_grey("Series", labels=c("centered", "non-centered")) +
  xlim(0.78, 1.6) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  ggtitle("B.") +
  theme(text = element_text(size=14, colour="black"))
a_df <- readRDS("../output/eight_schools_replicates_4_index.rds")

@@
